Analysis of epistatic inflation under large single additive effects, with a focus on the replication rate

### 2020-01-26 null_replication/docs/analyse_results.rmd
updated

```{r}
l <- list()
# load("../data/rs67903230.rdata")
# res$polygenic <- res$sim %% 2 == 0
# res$median_p_disc <- pchisq(res$lambda_disc * qchisq(0.5, 1), 1, low=FALSE)
# res$median_p_repl <- pchisq(res$lambda_repl * qchisq(0.5, 1), 1, low=FALSE)
# res$lambda_disc <- pnorm(1 - res$median_p_disc / 2)^2 / qchisq(0.5, 1)
# res$lambda_repl <- pnorm(1 - res$median_p_repl / 2)^2 / qchisq(0.5, 1)
# res$gene <- "MBNL1"
# res$i <- paste(res$gene, res$sentinel, res$cis, sep="_")
# res$scenario <- 1

@@

res <- bind_rows(l)

>>>>

First check the distribution under the null.

```{r}
library(dplyr)
load("../data/aggregate4.rdata")

hist(res$lambda_disc, breaks=40)
hist(res$lambda_disc2, breaks=40)

# chi(1) version of lambda
mean(res$lambda_disc)
sd(res$lambda_disc) / sqrt(nrow(res))

# chi(4) version of lambda
mean(res$lambda_disc2)
sd(res$lambda_disc2) / sqrt(nrow(res))
```

Can I convert the chi(1) lambda to the chi(4) lambda?

```{r}
res$lambda_disc

res$median_p_disc <- pchisq(res$lambda_disc * qchisq(0.5, 1), 1, low=FALSE)
res$median_f4_disc <- qf(res$median_p_disc, 4, 840, low=FALSE)
res$lambda_disc2_2 <- res$median_f4_disc / qchisq(0.5, 4, low=FALSE) * 4

plot(lambda_disc ~ lambda_disc2, res)
plot(lambda_disc2_2 ~ lambda_disc2, res)
```

Read in main results

```{r}
l <- list()

@@

res <- bind_rows(l)
res$median_p_disc <- pchisq(res$lambda_disc * qchisq(0.5, 1), 1, low=FALSE)
res$median_f4_disc <- qf(res$median_p_disc, 4, 840, low=FALSE)
res$lambda_disc <- res$median_f4_disc / qchisq(0.5, 4, low=FALSE) * 4
res$median_p_repl <- pchisq(res$lambda_repl * qchisq(0.5, 1), 1, low=FALSE)
res$median_f4_repl <- qf(res$median_p_repl, 4, 2112, low=FALSE)
res$lambda_repl <- res$median_f4_repl / qchisq(0.5, 4, low=FALSE) * 4
